Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex
Add convergence plot

We provide two examples of architectures learned by \textit{ShrinkNet}. One
for the best test available test accuracy and a slightly underperforming but
significantly (40x smaller that it's equivalent \textit{Static Network}). For
these two architectures we show the size at different time during training to
give a sense how the convergence happen.

\gl{Add the two plots}

>>>>

We provide two examples of architectures learned by \textit{ShrinkNet}. One
for the best test available test accuracy and a slightly underperforming but
significantly smaller that it's equivalent \textit{Static Network}. For
these two architectures we show the size at different time during training to
give a sense how the convergence happen.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{size_evolution}
\vspace*{-5mm} \caption{\label{network_size_evolution} Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy
} \end{center}
\vspace*{-4mm}
\end{figure}
